Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-11 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

@@

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 

@@

\caption{Block diagram for a typical stand-alone PV system (adapted from~\citep{Hansen}).}

@@

%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.40\textwidth]{equivckt1D}
\centering
\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\citep{Cubas}).}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

@@

%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

@@

In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}. In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to critical period method of sizing~\citep{Pinho}. 
%
In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed. 
%As a consequence, all the formulae of the employed mathematical models will also be updated. 
In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

@@

@@

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{tabular}{|c|c|c|c|c|c|}
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\subsection{Objectives and Setup}
\label{sec:setup}
Our \textcolor{red}{Verification and Simulation Results} aims to answer two research questions:
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------
We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.

@@

@@

We have considered five case studies, ranging from $700$ W to $1,200$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.

>>>>

\textcolor{red}{Here we compare model checking with simulation tool. However how they work is completely different. Simulation depends on the choice of input variables (and their values) in order to obtain the output. In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it. Therefore only with model checking we can prove the absence of system flaws.}

@@

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. \textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} %all the tools perform solar photovoltaic analysis; 

@@

\caption{\textcolor{red}{Block diagram for a typical stand-alone PV system, adapted from~\citep{Hansen}}.}

@@

%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.40\textwidth]{equivckt1D}
\centering
\caption{\textcolor{red}{1-diode equivalent PV cell/panel circuit model, adapted from~\citep{Cubas}.}}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

@@

\textcolor{red}{It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.}

%
The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

@@

In Step 1, the PV input data \textcolor{red}{(e.g., load power demand and load energy consumption)} 
and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}. In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to critical period method of sizing~\citep{Pinho}. 
%
In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed. 
%As a consequence, all the formulae of the employed mathematical models will also be updated. 
In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

@@

\textcolor{red}{Those estimated load curves are converted as vectors with 24 positions, one to each house of the day (in Watts): 
House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118]; 
House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136]; 
House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113]; 
House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207]; 
House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}

@@

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. \textcolor{red}{Power peak, power surge and energy consumption were estimated based on visiting and survey applied in each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah (4S)\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
\hline
\textcolor{red}{Power peak (W)}& 342  & 253  & 263 & 322 & 814 \\
\hline
\textcolor{red}{Power surge (W)}& 342 & 722 & 732 & 896 & 980\\
\hline
\makecell{Consumption \\ kWh/day}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\textcolor{red}{Legend: (S): Series; (P): Parallel.}
\end{scriptsize}
\end{table}
%------------------------------------------
\subsection{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
\textcolor{red}{We aim} to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------
We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified \textcolor{red}{four} threats to the validity of our results that can further be assessed.

@@

\textcolor{red}{
\textit{Simulation Tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification can change the comparative.}

@@

We have considered five case studies, ranging from $700$ W to $1,200$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
